---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

```{r loading, echo=TRUE}
## read from a connection to zip file
activity <- read.csv(unz(description = "activity.zip", filename = "activity.csv"), na.strings = "NA")
str(activity)
```

## What is mean total number of steps taken per day?

For this part of the assignment, you can ignore the missing values in the dataset.
```{r}
## index of valid rows (no NA)
ok_rows <- complete.cases(activity)
act <- activity[ok_rows, ]
```

1. Calculate the total number of steps taken per day
```{r total, echo=TRUE}
dsteps <- aggregate(steps ~ date, data = act, FUN = sum )
colnames(dsteps)[2] <- "SUM"
```

2. If you do not understand the difference between a histogram and a barplot, research the difference between them.
```{r barplot, echo=TRUE, fig.height=4}
barplot(height = dsteps$SUM, names.arg = dsteps$date, main = "Barplot of the total number of steps taken per day", xlab = "Date", ylab = "Steps per day")
```

Make a histogram of the total number of steps taken each day
```{r histogram, echo=TRUE, fig.height=7}
hist(dsteps$SUM, main = "Histogram of the total number of steps taken per day", xlab = "Total steps per day", labels = TRUE, col = "yellow")
```

3. Calculate and report the mean and median of the total number of steps taken per day

```{r mean, echo=TRUE}
MEAN <- as.character(round(mean(dsteps$SUM), 2))
MEDIAN <- as.character(round(median(dsteps$SUM), 2))
```
- Mean of the total number of steps per day: `r MEAN`
- Median of the total number of steps per day: `r MEDIAN`


## What is the average daily activity pattern?

1. Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)
```{r average, echo=TRUE}
act <- transform(act, interval=factor(interval))
avgsteps <- aggregate(steps ~ interval, act, FUN = mean )
plot(x = avgsteps$interval, y = avgsteps$steps, type = "l", main = "Average number of steps, across all days", ylab = "mean steps" )
lines(avgsteps)

```

2. Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
```{r interval, echo=TRUE}
maxstepsinterval <- levels(avgsteps$interval)[which.max(avgsteps$steps)]
```
- Interval that contains the maximum number of steps: `r maxstepsinterval`

## Imputing missing values

```{r imputting, echo=TRUE}
```



## Are there differences in activity patterns between weekdays and weekends?

```{r differences, echo=TRUE}
```
